\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage[hidelinks]{hyperref}
    \usepackage{xcolor}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=10in
    \pagestyle{empty}
    \raggedright

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\vspace*{-40pt}



%==== Profile ====%
\vspace*{-10pt}
\begin{center}
    {\Huge \scshape {Velislav Gerov}}\\
    London, United Kingdom $\cdot$ velislav.gerov@gmail.com $\cdot$ +44 7923 862 851 $\cdot$  \href{https://gerov.dev}{\underline{gerov.dev}}\\
\end{center}

%==== Experience ====%
\header{Experience}
\vspace{1mm}

\textbf{Walking on Earth} \hfill London, United Kingdom\\
\textit{Tech Lead} — {\sl React Native, React, GraphQL, Python, Django, PostgreSQL, AWS} \hfill Jan 2024 - Present\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
    \item Directed strategic security planning and vendor analysis, recommending concrete security enhancements to strengthen our cloud, application, and endpoint security.
    \item Streamlined mobile app development, achieving increase in development velocity and cost reductions by shifting from outsourced to in-house development under stringent deadlines.
    \item Managed a team of engineers of diverse skill sets, enhancing project estimation and technical leadership while fostering an environment of accountability and growth.
    \item  Boosted team morale and performance through continuous support and development opportunities, resulting in happier and more productive engineers.
\end{itemize}

\textit{Senior Full Stack Developer} — {\sl React, GraphQL, Python, Django, PostgreSQL, AWS} \hfill Mar 2023 - Dec 2023\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
    \item Pioneered the integration of wearable devices, expanding the system's capabilities to include advanced biometrics features and further enhance user engagement and system functionality.
    \item Led a six-engineer team through a multi-month rebranding initiative, ensuring timely and high-quality deliverables that aligned with strategic business goals.
    \item Championed the integration of advanced monitoring solutions across our technology stack, significantly enhancing early problem detection and response capabilities.
\end{itemize}

\textit{Full Stack Developer} — {\sl React, GraphQL, Python, Django, PostgreSQL, AWS} \hfill Jan 2022 - Apr 2023\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
    \item Owned and managed a suite of web applications, coordinating development efforts with outsourcing agencies to ensure high standards of quality and efficiency.
    \item Standardized development practices across teams, improving collaboration and project outcomes while securing infrastructure and hosting environments.
    \item Streamlined our infrastructure to enable automated service deployments, speeding up release cycles, reducing management overhead, and improving system scalability and reliability.
    \item Developed and launched an onboarding web experience that bridged the gap between web and mobile platforms, aligning user experiences across different mediums.
\end{itemize}

% Key Skills: \textit{Technical Leadership, Software Engineering, Software Engineering Management, Mobile Application Development, Cross-Platform Development, Security Enhancements}
% \vspace{2mm}

% Key Technologies: \textit{React Native, React, GraphQL, Python, Django, PostgreSQL, AWS}
% \vspace{2mm}

\textbf{Telebid Pro} \hfill Sofia, Bulgaria\\
\textit{Senior Software Developer}  — {\sl React, JavaScript, Perl, SQL}  \hfill Jun 2019 - Jun 2021\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
    \item Researched and developed a new database architecture to extend the capabilities of our accounting system and facilitate the creation of new modules and extensions.
    \item Took ownership and developed a new full-stack project where I introduced new front-end technologies to develop reliable accounting interfaces that ran in fast-paced environments.
    \item Extended the project with a new application designed for a specific embedded system as well as an API for communication between our services and several hardware devices.
    \item Devised a plan and lead a junior developer through it to introduce him to the project, ensuring that he learned best practices whilst making performance and extensibility improvements.
\end{itemize}


\textit{Software Developer}  — {\sl JavaScript, Perl, SQL, Redis, Systemd} \hfill Sep 2018 - May 2019\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
    \item Improved, expanded, and took ownership of an existing project that constituted a set of distributed services, front-ends, and APIs and was an integral part of several different projects.
    \item Designed and implemented a service by following strict requirements to make data available for a regulatory compliance scheme that allowed our clients to operate in a new market.
\end{itemize}

\textit{Junior Software Developer} — {\sl Python, JavaScript, Perl, SQL, Redis} \hfill May 2017 - Aug 2018\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
    \item As part of my onboarding I worked on a series of projects which include the development of an \href{https://github.com/velislavgerov/exercise02}{\underline{HTTP Web Server}} and an \href{https://github.com/velislavgerov/exercise03}{\underline{Online Shop}} which can be found via my \href{https://github.com/velislavgerov}{\underline{GitHub profile}}.
    \item Implemented a \href{https://github.com/velislavgerov/telebid-hackschool/tree/master/perl-json-diff}{\underline{Perl module}} that produces JSON Patch (RFC6902) difference between two JSON inputs which was integrated into our back-end and open-sourced on my \href{https://github.com/velislavgerov}{\underline{GitHub profile}}.
    \item Extended the capabilities of an existing project by developing a framework for integrating mathematical models as well as the relevant operational business logic and interfaces.
\end{itemize}

%==== Education ====%
\header{Education}
\textbf{University of Aberdeen}\hfill Aberdeen, Scotland\\
BSc Computing Science, Second Class Honours (Division One) \hfill Sep 2012 - Nov 2016\\
\vspace*{2mm}

{\textit{Single Honours Computing Project}} — {\sl JavaScript, C\#, ASP.NET MVC, NHibernate}\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
    \item Worked with the Aberdeen City Council\textquotesingle{}s Data Observatory Project in collaboration with Skills Development Scotland to create the initial dashboard for the \href{https://www.skillsdevelopmentscotland.co.uk/what-we-do/scotlands-careers-services/16plus-data-hub/}{\underline{16+ Data Hub}} portal.\\
\end{itemize}

{\textit{Research Methods Project}} — {\sl Linux, Apache, MySQL, PHP, AWS EC2 }\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
    \item Conducted a comparative study of popular PHP microframeworks to evaluate their relative performance in a Cloud environment.
\end{itemize}

{\textit{Software Engineering Team Project}} — {\sl C\#, Unity, Linux, Apache, MySQL, PHP}\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
    \item Collaborated with a team of students to develop a prototype for a 2D platformer game.
    \item Developed, deployed, and integrated the backend services which provided online capabilities.
\end{itemize}

%==== Projects ====%
\header{Projects}
{\textbf{Docxforms}} — {\sl TypeScript, Next.js, React, Bootstrap, Prisma} \hfill \href{https://docxforms.com/}{\underline{docxforms.com}}\\
Developed a tool to create web forms that fill and generate documents.
\vspace*{1mm}

{\textbf{Pattern Studio}} — {\sl JavaScript, React, Fabirc.js, Ant Design} \hfill \href{https://pattern-studio.gerov.dev/}{\underline{pattern-studio.gerov.dev}}\\
Developed an experimental pattern creation and print tool.
\vspace*{1mm}

{\textbf{Domestico}} — {\sl Magento2, ElasticSearch, Cloudinary} \hfill \href{https://domestico.bg/}{\underline{domestico.bg}}\\
Contributed to development planning, configuration, deployment, testing, and optimizations.
\vspace*{1mm}

%==== Certificates ====%
\header{Certificates}
\textbf{Mathematics for Machine Learning}\\
Specialization by Imperial College London on Coursera, Grade: 100.00\% \hfill Oct 2021\\
\vspace*{1mm}
\textbf{Machine Learning}\\
Course by Stanford University on Coursera, Grade: 100.00\% \hfill Jun 2021\\
\vspace*{1mm}
\textbf{Agile Software Development}\\
Course by Software University, Grade: 6.00/6.00 \hfill Mar 2020\\
\vspace*{1mm}

% \header{Technologies}
% \begin{tabular}{ l l }
% 	Programming Languages: & TypeScript, Python, Perl, SQL, Bash, C \\
% 	Front-end Stack:       & React, Material-UI, Bootstrap, Webpack \\
% 	Back-end Stack:        & Debian, PostgreSQL, Redis, Next.js     \\
% 	Cloud Environments:    & GitHub, Heroku, DigitalOcean           \\
% \end{tabular}
% \vspace{2mm}

\
\end{document}